Technical Report

### 2018-05-24 fully-abstract-comp/technical-report.tex

     By definition of $\codereg{\sigrets,\sigcloss,\mscode,\gc}$ and $H^\mathrm{code,\square}_\sigma$ and because we know that $\sigma\in\sigcloss$, it suffices to prove that
     one of the following holds: 
     \begin{itemize}
     \item $(\dom(\code) \mathrel{\#} \ta$ and $\npair[n']{(\vsc,\vsc)} \in \lrv \; \xi(\xi^{-1}(W))$
     \item $(\dom(\code) \subseteq \ta$ and $\npair[n']{(\vsc,\vsc)} \in \lrvtrusted \; \xi(\xi^{-1}(W))$
     \end{itemize}
     Since $\xi(\xi^{-1}(W)) = W$ and $\lrv \; W \subseteq \lrvtrusted \; W$ and because we know by assumption that $\dom(\mscode \mathrel{\#} \ta)$ or $\dom(\mscode) \subseteq \ta$, it suffices to prove that $\npair[n']{(\vsc,\vsc)} \in \lrv (W)$ in both cases.

     This follows by induction and Lemma~\ref{lem:downwards-closed} (if $\vsc \not\in \overline{c_{\mathrm{import}}}$) or by assumption (if $\vsc \in \overline{c_{\mathrm{import}}}$).

>>>>

     By definition of $\codereg{\sigrets,\sigcloss,\mscode,\gc}$ and $H^\mathrm{code,\square}_\sigma$ and because we know that $\sigma\in\sigcloss$, it suffices to prove that
     one of the following holds: 
     \begin{itemize}
     \item $(\dom(\code) \mathrel{\#} \ta$ and $\npair[n']{(\vsc,\vsc)} \in \lrv \; \xi(\xi^{-1}(W))$
     \item $(\dom(\code) \subseteq \ta$ and $\npair[n']{(\vsc,\vsc)} \in \lrvtrusted \; \xi(\xi^{-1}(W))$
     \end{itemize}
     Since $\xi(\xi^{-1}(W)) = W$ and $\lrv \; W \subseteq \lrvtrusted \; W$ and because we know by assumption that $\dom(\mscode \mathrel{\#} \ta)$ or $\dom(\mscode) \subseteq \ta$, it suffices to prove that $\npair[n']{(\vsc,\vsc)} \in \lrv (W)$ in both cases.
     This follows by induction and Lemma~\ref{lem:downwards-closed} (if $\vsc \not\in \overline{c_{\mathrm{import}}}$) or by assumption (if $\vsc \in \overline{c_{\mathrm{import}}}$), we know that $\npair[n']{(\vsc,\vsc)} \in \lrv(W)$.
